Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-14 Document/paper.tex
edit

\title[The shape of dark matter haloes in the AURIGA simulations]
{Dark Matter halo shape in the AURIGA simulations: radial
  dependence, time evolution and correlation with baryonic disk
  properties}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

% Abstract of the paper
\begin{abstract}
We present shape measurements of dark matter halos in a suit
of 30 cosmological simulations from the Auriga project.
One half of the Auriga simulations include Magnetohydrodynamics and stellar
formation, the other half is performed in a dark matter only setting.
We find a strong influence of baryons in making dark matter halos rounder at all
radii compared to its dark matter only counterparts.
This change in triaxility its more pronounced towards the inner
regions of the halo.
At distances close to the disk rounder dark matter distributions
correlate with massive stellar disks and low gas density.
The dark matter shape shows a strong alignment with the
stellar disk shape as a function of radius, the stronger aligmnet is
found at $~50$kpc, this alignment weakens at smaller and larger radii. 
In dark matter only simulations the time evolution of the shape
measured at the virial radius correlates with the radial shape
evolution at present day.  
However, this correlation is lost once the baryonic effects are
included. 
We conclude that in our simulation suite that baryonic physics
produces rounder halos with a strong correlation between its inner
shape and the stellar and gaseous properties of the disk.
\end{abstract}

>>>>

\title[The shape of dark matter haloes in the Auriga simulations]
{Dark matter halo shape in the Auriga simulations: radial
  dependence, time evolution and correlation with baryon disk
  properties}
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\'a, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

% Abstract of the paper
\begin{abstract}
We present shape measurements of dark matter halos in a suit
of 30 cosmological simulations from the Auriga project.
For all measurements we compare the results with full
magnetohydrodynamics and dark matter only physics.
We find a strong influence of baryons in making dark matter halos rounder at all
radii compared to its dark matter only counterparts.
This change in triaxility its more pronounced towards the inner
regions of the halo.
At distances close to the disk rounder dark matter distributions
correlate with massive stellar disks and low gas density.
The dark matter shape shows a strong alignment with the
stellar disk shape as a function of radius, the stronger aligmnet is
found at $~50$kpc, this alignment weakens at smaller and larger radii. 
In dark matter only simulations the time evolution of the shape
measured at the virial radius correlates with the radial shape
evolution at present day.  
However, this correlation is lost once the baryonic effects are
included. 
We conclude that in our simulation suite that baryonic physics
produces rounder halos with a strong correlation between its inner
shape and the stellar and gaseous properties of the disk.
\end{abstract}
